---
title: "p8105_hw1_yw3236"
output: github_document
author: "Yishan Wang"
date: 2018-09-21
---
# Set Up

First, I went to GitHub to create a new public repo named p8105_hw1.

Second, I created a local R project named p8105_hw1 by using File > New Project > Version Control and providing the repo URL.

Third, I created a .Rmd file named p8105_hw1_yw3236 by using File > New File > R Markdown File.

Forth, I used `output: github_document` to render a .Rmd file to a .md file.

# Problem 1

Create a data frame comprised of:

  * A random sample of size 10 from a uniform[0, 5] distribution
  * A logical vector indicating whether elements of the sample are greater than 2
  * A (length-10) character vector
  * A (length-10) factor vector

```{r set_up, include = FALSE}
library(tidyverse)
```

```{r create r data frame}
set.seed(1)

df = tibble(
  vec_numeric = runif(10, min = 0, max = 5),
  vec_logical = c(vec_numeric > 2),
  vec_char = c("I", "love", "data", "science", "very", "much", "it", "is", "so", "wonderful"),
  vec_factor = c("yes", "yes", "yes", "no", "no", "no", "yes", "yes", "no", "no")
)
```

Take the mean of each variable in the data frame.

```{r take mean, warning = FALSE}
mean(df$vec_numeric)
mean(df$vec_logical)
mean(df$vec_char)
mean(df$vec_factor)
```

For calculating mean, numeric and logical variable work, but char and factor variable don't work. The reason is that numerical and logical variables can be transfered to numerical value, but char and factor variables can't be transfered to numerical value. After transfering to numerical value, R can calculate the mean of the variable.

Convert variables from one type to another.

```{r convert variable_1, warning = FALSE, results = 'hide'}
as.numeric(df$vec_logical)
as.numeric(df$vec_char) 
as.numeric(df$vec_factor)
```

Only logical variable can be converted to numerical variable. Both char and factor variables are not able to be contverted (NA).

```{r convert variable_2, warning = FALSE}
as.numeric(as.factor(df$vec_char))
as.numeric(as.character(df$vec_factor))
```

Charactor variable can be converted from charactor to factor to numeric. 
Factor variable can't be converted from factor to character to numeric.