---
title: "p8105_hw1_yw3236"
output: github_document
author: "Yishan Wang"
date: 2018-09-21
---
# Set Up

First, I went to GitHub to create a new public repo named p8105_hw1.

Second, I created a local R project named p8105_hw1 by using File > New Project > Version Control and providing the repo URL.

Third, I created a .Rmd file named p8105_hw1_yw3236 by using File > New File > R Markdown File.

Forth, I used `output: github_document` to render a .Rmd file to a .md file.

# Problem 1

Create a data frame comprised of:

  * A random sample of size 10 from a uniform[0, 5] distribution
  * A logical vector indicating whether elements of the sample are greater than 2
  * A (length-10) character vector
  * A (length-10) factor vector

```{r set_up, include = FALSE}
library(tidyverse)
```

```{r create r data frame}
set.seed(1)

df = tibble(
  vec_numeric = runif(10, min = 0, max = 5),
  vec_logical = c(vec_numeric > 2),
  vec_char = c("I", "love", "data", "science", "very", "much", "it", "is", "so", "wonderful"),
  vec_factor = c("yes", "yes", "yes", "no", "no", "no", "yes", "yes", "no", "no")
)
```

Take the mean of each variable in the data frame.

```{r take mean, warning = FALSE}
mean(df$vec_numeric)
mean(df$vec_logical)
mean(df$vec_char)
mean(df$vec_factor)
```
